Multilevel generalizations of collective spin dynamics and squeezing

### 2020-08-19 sun_phases/multilevel_spin_notes.tex
minor fix

where $\p{S_\z,S_\x,S_\y} \equiv \xi_1\times\p{D_{1,0},D_{1,1},D_{1,-1}}$ is the standard $\mathfrak{su}(2)$ subalgebra of the operators on a single $n$-level spin, and

@@

\begin{table}
  \centering
  \caption{Drive Hamiltonians that can be implemented with various amplitude-matching conditions.}
  \begin{tabular}{c|c|c}
    Condition & $\p{h_0,h_+,h_-}/h$
    & $H_{\t{Raman}}^{\t{single}}/\p{h^2/\Delta}$
    \\ \hline\hline
    $\Omega_0=\pm\Omega_+=\pm\Omega_-$ & $\p{1,\pm\sqrt{2},0}$
    & $\pm\sqrt{2} S_\x + \p{S_\x^2 - S_\y^2}$
    \\ \hline
    $\Omega_0=\pm\Omega_+=\mp\Omega_-$ & $\p{1,0,\pm\sqrt{2}}$
    & $\pm\sqrt{2}\p{S_\z S_\x + S_\x S_\z} - \p{S_\x^2-S_\y^2}$
    \\ \hline
    $\Omega_0=\Omega_\mp=0$ & $\p{0,1,\pm1}$
    & $\pm S_\z + S_\z^2$
    \\ \hline
    $\sqrt{2}\Omega_0=\pm\Omega_+=\pm\Omega_-$
    & $\p{1,\pm1,0}$ & $\pm S_\x + S_\x^2$
    \\ \hline
    $\sqrt{2}\Omega_0=\pm\Omega_+=\mp\Omega_-$
    & $\p{1,0,\pm1}$ & $\pm\p{S_\z S_\x+S_\x S_\z} + S_\y^2$
    \\ \hline
    $\Omega_+=\Omega_-=0$ & $\p{1,0,0}$ & $-S_\z^2$
    \\ \hline
    $\Omega_0=0$,  $\Omega_+=+\Omega_-$ & $\p{0,1,0}$ & $-S_\y^2$
    \\ \hline
    $\Omega_0=0$,  $\Omega_+=-\Omega_-$ & $\p{0,0,1}$ & $-S_\x^2$
  \end{tabular}
  \label{tab:drives}
\end{table}

>>>>

where $\v S = \p{S_\z,S_\x,S_\y} \equiv \xi_1\times\p{D_{1,0},D_{1,1},D_{1,-1}}$ is the standard $\mathfrak{su}(2)$ subalgebra of the operators on a single $n$-level spin, and

@@

\begin{table}
  \centering
  \caption{Drive Hamiltonians that can be implemented with various amplitude-matching conditions.}
  \begin{tabular}{c|c|c}
    Condition & $\p{h_0,h_+,h_-}/h$
    & $H_{\t{Raman}}^{\t{single}}/\p{h^2/\Delta}$
    \\ \hline\hline
    $\Omega_0=\pm\Omega_+=\pm\Omega_-$ & $\p{1,\pm\sqrt{2},0}$
    & $\pm\sqrt{2} S_\x + \p{S_\x^2 - S_\y^2}$
    \\ \hline
    $\Omega_0=\pm\Omega_+=\mp\Omega_-$ & $\p{1,0,\pm\sqrt{2}}$
    & $\pm\sqrt{2}\p{S_\z S_\x + S_\x S_\z} - \p{S_\x^2-S_\y^2}$
    \\ \hline
    $\Omega_0=\Omega_\mp=0$ & $\p{0,1,\pm1}$
    & $\pm S_\z + S_\z^2 - \v S^2$
    \\ \hline
    $\sqrt{2}\Omega_0=\pm\Omega_+=\pm\Omega_-$
    & $\p{1,\pm1,0}$ & $\pm S_\x + S_\x^2$
    \\ \hline
    $\sqrt{2}\Omega_0=\pm\Omega_+=\mp\Omega_-$
    & $\p{1,0,\pm1}$ & $\pm\p{S_\z S_\x+S_\x S_\z} + S_\y^2$
    \\ \hline
    $\Omega_+=\Omega_-=0$ & $\p{1,0,0}$ & $-S_\z^2 + \v S^2$
    \\ \hline
    $\Omega_0=0$,  $\Omega_+=+\Omega_-$ & $\p{0,1,0}$ & $-S_\y^2$
    \\ \hline
    $\Omega_0=0$,  $\Omega_+=-\Omega_-$ & $\p{0,0,1}$ & $-S_\x^2$
  \end{tabular}
  \label{tab:drives}
\end{table}
